A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Clarify that it's horrible when programs diverge.

\begin{code}
main = do
  captured <- randomRIO (False, True)

  runApp config $ do
    diverged <- export $ \transmitted -> do
      if captured == transmitted
        then return ``All OK''
        else return ``Diverged''

    runClient $ do
      divergence <- onServer (diverged <.> captured)
      alert divergence
\end{code}

The dialog box displayed by this program will read ``All OK'' roughly half
of the times it is run, while in half of the runs it will read ``Diverged''.
The reason for this is that the \lstinline!randomRIO! computation will be
executed twice - once on the client, and once on the server. Whenever the
computation returns differening results, the client and the server will have
conflicting opinions on the actual value of \lstinline!captured!, causing any
code which - quite reasonably - assumes that variables are consistent between
client and server to fail.

>>>>

\begin{code}
main = do
  exportTwo <- randomRIO (False, True)

  runApp config $ do
    when exportTwo $ do
      _ <- export (return () :: Server ())
      return ()
    fun <- export $ return "I'm a little teapot"

    runClient $ do
      onServer fun >>= alert
\end{code}

Whenever \lstinline!exportTwo! gets assigned a \lstinline!True! value, this
application will call \lstinline!export! twice, assigning the identifier
\lstinline!0! to the first exported computation, which is discarded, and
\lstinline!1! to the second, \lstinline!fun!, which is kept and invoked.
If, on the other hand, \lstinline!exportTwo! is \lstinline!False!,
only the second computation will be exported, and will thus be assigned the
identifier \lstinline!1!.

This is perfectly fine as long as the client and server both assign the
same identifier to \lstinline!fun!. However, since \lstinline!randomRIO! is
not deterministic and since all computations called by \lstinline!main! will be
executed on both the client and the server, there is a possibility that
\lstinline!fun! will be assigned the identifier \lstinline!0! on the client and
\lstinline!1! on the server. In this scenario, when the client attempts to call
the \lstinline!return "I'm a little teapot"! computation over the network,
the server instead executes the \lstinline!return ()! computation, which
returns \lstinline!()! rather than \lstinline!String!, breaking the type safety
of our program!
